Fixing Vulnerabilities Hinders Maintainability

### 2020-01-31 paper/icpc20.tex
new version

\subsubsection*{\textit{\textbf{RQ1} What is the impact of security patches on the
maintainability of open-source software?}}

Often security flaws require patching code to make software more secure.
However, \textbf{there is no evidence yet of how security patches impact the
maintainability of open-source software}. Our suspicion is that developers tend
to introduce technical debt in their software when patching the code base to
address a security flaw because they tend to choose the easiest path to solve
it. To address it, we compute the maintainability of $1037$ commits using the
\emph{Better Code Hub} tool. 
%
\subsubsection*{\textit{\textbf{RQ2}  Which patterns of security patches are more likely to
affect open-source software maintainability?}}

@@

\subsubsection*{\textit{\textbf{RQ3} What is the impact of security patches versus regular changes on the
maintainability of open-source software?}}

@@

\subsubsection*{\textit{\textbf{RQ1} What is the impact of security patches on the
maintainability of open-source software?}}

@@

\subsubsection*{\textit{\textbf{RQ2} Which patterns of security patches are more likely to
affect open-source software maintainability?}}

@@

\subsubsection*{\textit{\textbf{RQ3} What is the impact of security patches versus regular changes on the
maintainability of open-source software?}}

>>>>

Often security flaws require patching code to make software more secure.
However, \textbf{there is no evidence yet of how security patches impact the
maintainability of open-source software}. Our suspicion is that developers tend
to introduce technical debt in their software when patching the code base to
address a security flaw because they tend to choose the easiest path to solve
it. To address it, we compute the maintainability of $1037$ commits using the
\emph{Better Code Hub} tool. 
%
\subsubsection*{\textit{\textbf{RQ2}  \textbf{Which patterns of security patches are more likely to
affect open-source software maintainability?}}}

@@

\subsubsection*{\textit{\textbf{RQ3} \textbf{What is the impact of security patches versus regular changes on the
maintainability of open-source software?}}}

@@

@@

@@

\subsubsection*{\textit{\textbf{RQ3} \textbf{What is the impact of security patches versus regular changes on the
maintainability of open-source software?}}}
